Intelligent Reflecting Surface-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design

### 2020-11-23 main.tex
:pencil: Rephrase system model

		As shown in Fig.~\ref{fi:system}, we propose an IRS-aided SWIPT system where a $M$-antenna AP delivers information and power simultaneously, through a $L$-element IRS, to a single-antenna user over $N$ orthogonal evenly-spaced subbands at frequency $f_n$ ($n=1,\dots,N$). We consider a quasi-static block fading channel model and focus on one particular block where the channel responses are constant. It is assumed that the perfect Channel State Information (CSI) of all links with negligible training overhead is known at the AP. Two practical co-located receiver architectures, namely TS and PS, are compared in terms of the R-E region. Specifically, TS divides each time slot into orthogonal data and energy slots and performs a time sharing between WPT and Wireless Information Transfer (WIT). In comparison, PS splits the received signal into individual ID and EH streams such that the splitting ratio $\rho$ is coupled with waveform and beamforming design. Signals reflected by the IRS for two and more times are omitted, and the noise power is assumed too small to be harvested.

		\begin{subsection}{Transmit Signal}
			Denote $\tilde{x}_{I,n}(t)$ as the information symbol transmitted over subband $n$ satisfying $\tilde{x}_{I,n}\sim\mathcal{CN}(0,1)$. The superposed transmit signal on antenna $m$ ($m=1,\dots,M$) at time $t$ is
			\begin{equation}\label{eq:x_m}
				x_m(t)=\Re\left\{\sum_{n=1}^N\left({w_{I,n,m}\tilde{x}_{I,n}(t)}+w_{P,n,m}\right){e^{j2{\pi}{f_n}{t}}}\right\}
			\end{equation}
			where $w_{I/P,n,m}$ denotes the weight of the information and power signal transmitted by antenna $m$ at subband $n$.

			Stacking up the entries on all antennas, we define $\boldsymbol{w}_{I/P,n}=[w_{I/P,n,1},\dots,w_{I/P,n,M}]^T \in \mathbb{C}^{M \times 1}$ and $\boldsymbol{x}(t)=\boldsymbol{x}_{I}(t)+\boldsymbol{x}_{P}(t)$, where
			\begin{align}
				\boldsymbol{x}_{I}(t) &= \Re{\left\{\sum_{n=1}^N\boldsymbol{w}_{I,n}\tilde{x}_{I,n}(t){e^{j2{\pi}{f_n}{t}}}\right\}}\,,\label{eq:x_I}\\
				\boldsymbol{x}_{P}(t) &= \Re{\left\{\sum_{n=1}^N\boldsymbol{w}_{P,n}{e^{j2{\pi}{f_n}{t}}}\right\}}\,.\label{eq:x_P}
			\end{align}
		\end{subsection}

		\begin{subsection}{Composite Channel}
			At subband $n$, denote the AP-user direct channel as $\boldsymbol{h}_{D,n}^H \in \mathbb{C}^{1 \times M}$, AP-IRS incident channel as $\boldsymbol{H}_{I,n} \in \mathbb{C}^{L \times M}$, and IRS-user reflective channel as $\boldsymbol{h}_{R,n}^H \in \mathbb{C}^{1 \times L}$. At the IRS, element $l$ ($l=1,\dots,L$) redistributes the incoming signal by adjusting the reflection coefficient $\phi_l=\alpha_l e^{j\theta_l}$ with reflection amplitude $\alpha_l \in [0,1]$ and phase shift $\theta_l \in [0,2\pi)$~\footnote{To investigate the performance upper bound of IRS, we suppose the reflection coefficient is maximized $\alpha_l=1\,,\forall l$ while the phase shift is a continuous variable over $[0,2\pi)$.}. Define the IRS matrix as $\boldsymbol{\Theta} = \mathrm{diag}(\phi_1, \dots, \phi_L) \in \mathbb{C}^{L \times L}$ that collects the reflection coefficients onto its main diagonal entries. The auxiliary link introduced by IRS can be modeled as a concatenation of the AP-IRS incident channel, IRS reflection matrix, and IRS-user reflective channel. On top of this, the total composite channel is obtained by superposing the IRS-aided auxiliary channel to the AP-user direct channel as
			\begin{equation}\label{eq:h_n}
				\boldsymbol{h}_{n}^H = \boldsymbol{h}_{D,n}^H + \boldsymbol{h}_{R,n}^H \boldsymbol{\Theta} \boldsymbol{H}_{I,n} = \boldsymbol{h}_{D,n}^H + \boldsymbol{\phi}^H \boldsymbol{V}_{n}
			\end{equation}
			where $\boldsymbol{\phi}=[\phi_1, \dots, \phi_L]^H \in \mathbb{C}^{L \times 1}$ and $\boldsymbol{V}_{n}=\mathrm{diag}(\boldsymbol{h}_{R,n}^H)\boldsymbol{H}_{I,n} \in \mathbb{C}^{L \times M}$. Note the conjugate transpose in the notation of $\boldsymbol{\phi}$ makes its entries the complex conjugate of the diagonal entries of $\boldsymbol{\Theta}$.
			\begin{remark}\label{re:irs_frequency_flat}
				Due to hardware constraints, independent phase shift control for different frequencies is prohibited and the IRS is frequency-flat. Hence, the auxiliary channels at different frequencies cannot be simultaneously maximized and there is a tradeoff in subchannel alignment.
				% At subband $n$, the AP-IRS MIMO channel $\boldsymbol{H}_{I,n}$ can be divided into $L$ MISO channels between all transmit antennas and each IRS element. Reflection coefficient $\phi_l$ is shared for the $l$-th AP-IRS MISO channel of all subbands, namely $MN$ entries in total.
				The reflection coefficient of each IRS element is shared for the AP-IRS MISO channel and over all subbands, namely $MN$ entries in total.
			\end{remark}
		\end{subsection}

		\begin{subsection}{Receive Signal}
			At the single-antenna receiver, the total received signal $y(t)=y_I(t)+y_P(t)$ captures the contribution from information and power components over $N$ subbands, where
			\begin{align}
				y_{I}(t) & = \Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{n}^H}{\boldsymbol{w}_{I,n}\tilde{x}_{I,n}(t)}{e^{j2{\pi}{f_n}{t}}}\right\}\,,\label{eq:y_I}\\
				y_{P}(t) & = \Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{n}^H}\boldsymbol{w}_{P,n}{e^{j2{\pi}{f_n}{t}}}\right\}\,.\label{eq:y_P}
			\end{align}
		\end{subsection}

		\begin{subsection}{Information Decoder}
			A major benefit of the superposed waveform is that the multisine power waveform creates no interference to the information waveform. Therefore, the achievable rate writes as
			\begin{equation}\label{eq:R}
				R(\boldsymbol{\phi},\boldsymbol{w}_I,\rho) = \sum_{n=1}^N{\log_2\left(1+\frac{(1-\rho)\lvert \boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n} \rvert^2}{\sigma_n^2}\right)}
			\end{equation}
			where $\rho$ is the power splitting ratio for the energy harvester, $\sigma_n^2$ is the variance of the total noise (at RF-band and during RF-to-baseband conversion) on tone $n$. Rate \eqref{eq:R} is achievable with either waveform cancellation or translated demodulation \cite{Clerckx2018b}.
		\end{subsection}

		\begin{subsection}{Energy Harvester}
			\begin{figure}[!t]
				\centering
				\noindent
				\begin{minipage}[b]{0.5\linewidth}
					\centering
					\subfloat[Antenna equivalent circuit\label{ci:antenna_equivalent_circuit}]{
						\resizebox{0.9\linewidth}{!}{
							\begin{circuitikz}[transform shape]
							\draw (0,0) to [sV=$v_s$] (0,2);
							\draw (0,2) to [short] (1,2);
							\draw (1,2) to [R=$R_\text{ant}$] (3,2);
							\draw (3,2) to [short] (4,2);
							\draw (4,2) to [R=$R_\text{in}$, v<=$v_{\text{in}}$] (4,0);
							\draw (4,0) to [short] (2,0) node[ground](GND){};
							\draw (2,0) to [short] (0,0);
						\end{circuitikz}
						}
					}
				\end{minipage}%
				\begin{minipage}[b]{0.5\linewidth}
					\centering
					\subfloat[A single diode rectifier\label{ci:single_diode_rectifier}]{
						\resizebox{0.9\linewidth}{!}{
							\begin{circuitikz}[transform shape]
							\draw (0,0) to [sV=$v_\text{in}$] (0,2);
							\draw (0,2) to [short] (0.25,2);
							\draw (0.25,2) to [D, v<=$v_d$, i=$i_d$] (2.25,2);
							\draw (2.25,2) to [short, -*] (2.5,2);
							\draw (2.5,2) to [C, l_=$C$, -*] (2.5,0);
							\draw (2.5,2) to [short] (4,2);
							\draw (4,2) to [R=$R_L$, v<=$v_{\text{out}}$, i=$i_{\text{out}}$] (4,0);
							\draw (4,0) to [short] (2,0) node[ground](GND){};
							\draw (2,0) to [short] (0,0);
						\end{circuitikz}
						}
					}
				\end{minipage}
				\caption{Rectenna circuits.}
			\end{figure}

			In this section, we briefly revisit a tractable nonlinear rectenna model that relates the harvester output DC current to the received waveform \cite{Clerckx2016a,Clerckx2018b}. Fig.~\ref{ci:antenna_equivalent_circuit} illustrates the equivalent circuit of a lossless antenna, where the incoming signal creates an voltage source $v_s(t)$ and the antenna has an impedance $R_{\text{ant}}$. Let $R_{\text{in}}$ be the total input impedance of the rectifier and matching network, and we assume the voltage across matching network is negligible. When perfectly matched ($R_{\text{in}}=R_{\text{ant}}$), the rectifier input voltage is $v_{\text{in}}(t)=y(t)\sqrt{\rho R_{\text{ant}}}$.

			Rectifiers consist of nonlinear components as diode and capacitor to produce DC output and store energy \cite{Pinuela2013}. Consider a simplified rectifier model in Fig.~\ref{ci:single_diode_rectifier} where a single series diode is followed by a low-pass filter with a parallel load. Denote $i_s$ as the reverse bias saturation current, $n'$ as the diode ideality factor, $v_t$ as the thermal voltage, $v_d(t)=v_{\text{in}}(t)-v_{\text{out}}(t)$ as the voltage across the diode where $v_{\text{out}}(t)$ is the output voltage across the load. A Taylor expansion of the diode characteristic equation $i_d(t)=i_s(e^{v_d(t)/n' v_t}-1)$ around a quiescent operating point $a$ writes as $i_d(t)=\sum_{i=0}^{\infty}k_i'(v_d(t)-a)^i$, where $k_0'=i_s(e^{a/n' v_t}-1)$ and $k_i'=i_se^{a/n'v_t}/i!(n'v_t)^i$ for $i=1,\dots,\infty$. Note that this small-signal expansion model is only valid for the non-linear operation region, and the I-V relationship would be linear if the diode behavior is dominated by the load \cite{Clerckx2016a}. Also, an ideal low-pass filter with steady-state response can provide a constant $v_{\text{out}}$ that depends on the peak of $v_{\text{in}}(t)$ \cite{Curty2005}. Therefore, a proper choice of the operating voltage drop is $a=\mathcal{E}\{v_d(t)\}=-v_{\text{out}}$ such that
			\begin{equation}\label{eq:i_d}
				i_d(t)=\sum_{i=0}^{\infty}k_i'\rho^{i/2}R_{\text{ant}}^{i/2}y(t)^i\,.
			By discarding the non-DC components, taking an expectation over symbol distribution, and truncating \eqref{eq:i_d} to the $n_0$-th order, we approximate the average output DC current for a given channel as
			\begin{equation}\label{eq:i_out}
				i_{\text{out}}(t)=\mathcal{A}\{i_d(t)\}\approx\sum_{i=0}^{n_0}{k_i'}{\rho^{i/2}}{R_{\text{ant}}^{i/2}}\mathcal{E}\left\{{\mathcal{A}\left\{y(t)^i\right\}}\right\}\,.
			With the assumption of evenly-spaced frequencies, it holds that $\mathcal{A}\left\{y(t)^i\right\}=0$ for odd $i$ thus the related terms have no contribution to DC output. However, $k_i'$ is still a function of $i_{\text{out}}$, and \cite{Clerckx2016a} proved that maximizing a truncated $i_{\text{out}}$ is equivalent to maximizing a monotonic function
			\begin{equation}\label{eq:z}
				z(\boldsymbol{\phi},\boldsymbol{w}_I,\boldsymbol{w}_P,\rho)=\sum_{i\,\text{even},i\ge2}^{n_0}{k_i}{\rho^{i/2}}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{\mathcal{A}\left\{y(t)^i\right\}\right\}}
			where $k_i=i_s/i!(nv_t)^i$. It can be observed that the traditional linear harvester model, where the output DC power equals the sum of the power harvested on each frequency, is a special case of \eqref{eq:z} with $n_0=2$. However, due to the coupling among different frequencies, some high-order AC components compensate each other and further contribute to the output DC power. In other words, even-order terms with $i \ge 4$ account for the nonlinear behavior of the diode. For simplicity, we let $\beta_2={k_2}{R_{\text{ant}}}$, $\beta_4={k_4}{R_{\text{ant}}^2}$ and choose $n_0=4$ to investigate fundamental rectifier nonlinearity so that $z$ further reduces to \eqref{eq:z_expand}. Note that $\mathcal{E}\left\{\lvert\tilde{x}_{I,n}\rvert^2\right\}=1$ but $\mathcal{E}\left\{\lvert\tilde{x}_{I,n}\rvert^4\right\}=2$, which can be interpreted as a modulation gain on the nonlinear terms of the output DC current. Inspired by \cite{Huang2017}, we stack up channel and waveform vectors over all subbands as $\boldsymbol{h}=[\boldsymbol{h}_1^T,\dots,\boldsymbol{h}_N^T]^T \in \mathbb{C}^{MN \times 1}$ and $\boldsymbol{w}_{I/P}=[\boldsymbol{w}_{I/P,1}^T,\dots,\boldsymbol{w}_{I/P,N}^T]^T \in \mathbb{C}^{MN \times 1}$. On top of this, let $\boldsymbol{W}_{I/P}=\boldsymbol{w}_{I/P}\boldsymbol{w}_{I/P}^H \in \mathbb{C}^{MN \times MN}$. As illustrated by Fig.~\ref{fi:block_diagonal}, $\boldsymbol{W}_{I/P}$ can be divided into $N \times N$ blocks of size $M \times M$, and we let $\boldsymbol{W}_{I/P,k}$ keep its $k$-th ($k=-N+1,\dots,N-1$) block diagonal and set all other blocks to $\boldsymbol{0}^{M \times M}$. Hence, the components of the output DC current $z$ can be expressed in \eqref{eq:y_I2} -- \eqref{eq:y_P4}.

			\begin{figure*}[!t]
				\begin{equation*}
						\boldsymbol{W}_{I/P}=
						\begin{tikzpicture}[>=stealth,thick,baseline,every right delimiter/.append style={name=rd},]
							\matrix [matrix of math nodes,left delimiter=(,right delimiter=)] (m)
							{
								\boldsymbol{w}_{I/P,1}\boldsymbol{w}_{I/P,1}^H & \boldsymbol{w}_{I/P,1}\boldsymbol{w}_{I/P,2}^H & \dots & \boldsymbol{w}_{I/P,1}\boldsymbol{w}_{I/P,N}^H \\
								\boldsymbol{w}_{I/P,2}\boldsymbol{w}_{I/P,1}^H & \boldsymbol{w}_{I/P,2}\boldsymbol{w}_{I/P,2}^H & \ddots & \vdots \\
								\vdots & \ddots & \ddots & \boldsymbol{w}_{I/P,N-1}\boldsymbol{w}_{I/P,N}^H \\
								\boldsymbol{w}_{I/P,N}\boldsymbol{w}_{I/P,1}^H & \dots & \boldsymbol{w}_{I/P,N}\boldsymbol{w}_{I/P,N-1}^H & \boldsymbol{w}_{I/P,N}\boldsymbol{w}_{I/P,N}^H \\
							};
							\draw[dotted,thick] (m-4-1.north west) rectangle (m-4-1.south east);
							\draw[dotted,thick,fill=gray,opacity=0.125] (m-2-1.north west) rectangle (m-2-1.south east); \draw[dotted,thick,fill=gray,opacity=0.125] (m-3-2.north west) rectangle (m-3-2.south east); \draw[dotted,thick,fill=gray,opacity=0.125] (m-4-3.north west) rectangle (m-4-3.south east);
							\draw[dashed,thick,fill=gray,opacity=0.5] (m-1-1.north west) rectangle (m-1-1.south east); \draw[dashed,thick,fill=gray,opacity=0.5] (m-2-2.north west) rectangle (m-2-2.south east); \draw[dashed,thick,fill=gray,opacity=0.5] (m-3-3.north west) rectangle (m-3-3.south east); \draw[dashed,thick,fill=gray,opacity=0.5] (m-4-4.north west) rectangle (m-4-4.south east);
							\draw[solid,thick,fill=gray,opacity=0.25] (m-1-2.north west) rectangle (m-1-2.south east); \draw[solid,thick,fill=gray,opacity=0.25] (m-2-3.north west) rectangle (m-2-3.south east); \draw[solid,thick,fill=gray,opacity=0.25] (m-3-4.north west) rectangle (m-3-4.south east);
							\draw[solid,thick] (m-1-4.north west) rectangle (m-1-4.south east);
							\draw[<-] (m-4-3.south|-m.south) -- ++(0.5,-0.15) node[below]{$k=-1$};
							\draw[<-] (rd.east|-m.south) -- ++(0.5,-0.15) node[right]{$k=0$};
							\draw[<-] (rd.east|-m-3-4.east) -- ++(0.5,-0.15) node[right]{$k=1$};

>>>>

		As shown in Fig.~\ref{fi:system}, we propose an IRS-aided SWIPT system where a $M$-antenna AP delivers information and power simultaneously, through a $L$-element IRS, to a single-antenna user over $N$ orthogonal evenly-spaced subbands at frequency $f_n$ ($n=1,\dots,N$). We consider a quasi-static block fading channel model and focus on one particular block where the channel responses are constant. It is assumed that the perfect Channel State Information (CSI) of all links with negligible training overhead is known at the AP. As two practical transceiving modes, TS and PS are compared in terms of the achievable R-E region. Specifically, TS divides each time slot into orthogonal data and energy slots and performs a time sharing between WPT and Wireless Information Transfer (WIT). In comparison, PS splits the received signal into individual ID and EH streams such that the splitting ratio $\rho$ is coupled with waveform and beamforming design. Signals reflected by the IRS for two and more times are omitted, and the noise power is assumed too small to be harvested.

		\begin{subsection}{Transmit Signal}
			Denote $\tilde{x}_{\text{I,}n}(t)$ as the information symbol transmitted over subband $n$ satisfying $\tilde{x}_{\text{I,}n}\sim\mathcal{CN}(0,1)$. The superposed transmit signal on antenna $m$ ($m=1,\dots,M$) at time $t$ is
			\begin{equation}\label{eq:x_m}
				x_m(t)=\Re\left\{\sum_{n=1}^N\left({w_{\text{I,}n,m}\tilde{x}_{\text{I,}n}(t)}+w_{\text{P,}n,m}\right){e^{j2{\pi}{f_n}{t}}}\right\}
			\end{equation}
			where $w_{\text{I/P,}n,m}$ denotes the weight of the information/power signal transmitted by antenna $m$ at subband $n$. Stacking up the entries on all transmit antennas, we further define $\boldsymbol{w}_{\text{I/P,}n} \triangleq [w_{\text{I/P,}n,1},\dots,w_{\text{I/P,}n,M}]^T \in \mathbb{C}^{M \times 1}$ and $\boldsymbol{x}(t) \triangleq \boldsymbol{x}_{\text{I}}(t)+\boldsymbol{x}_{\text{P}}(t)$, where
			\begin{align}
				\boldsymbol{x}_{\text{I}}(t) &= \Re{\left\{\sum_{n=1}^N\boldsymbol{w}_{\text{I,}n}\tilde{x}_{\text{I,}n}(t){e^{j2{\pi}{f_n}{t}}}\right\}}\,,\label{eq:x_I}\\
				\boldsymbol{x}_{\text{P}}(t) &= \Re{\left\{\sum_{n=1}^N\boldsymbol{w}_{\text{P},n}{e^{j2{\pi}{f_n}{t}}}\right\}}\,.\label{eq:x_P}
			\end{align}
		\end{subsection}

		\begin{subsection}{Composite Channel}
			At subband $n$, we denote the AP-user direct channel as $\boldsymbol{h}_{\text{D,}n}^H \in \mathbb{C}^{1 \times M}$, AP-IRS incident channel as $\boldsymbol{H}_{\text{I,}n} \in \mathbb{C}^{L \times M}$, and IRS-user reflective channel as $\boldsymbol{h}_{\text{R,}n}^H \in \mathbb{C}^{1 \times L}$. At the IRS, element $l$ ($l=1,\dots,L$) redistributes the incoming signal by adjusting the reflection coefficient $\phi_l \triangleq \alpha_l e^{j\theta_l}$ with the reflection amplitude $\alpha_l \in [0,1]$ and phase shift $\theta_l \in [0,2\pi)$~\footnote{To investigate the performance upper bound of IRS, we suppose the reflection coefficient is maximized $\alpha_l=1\,,\forall l$ while the phase shift is a continuous variable over $[0,2\pi)$.}. Also, define the IRS matrix as $\boldsymbol{\Theta} \triangleq \mathrm{diag}(\phi_1, \dots, \phi_L) \in \mathbb{C}^{L \times L}$ that collects the reflection coefficients onto its main diagonal entries. The auxiliary link introduced by IRS can be modeled as a concatenation of the AP-IRS incident channel, IRS reflection matrix, and IRS-user reflective channel. On top of this, the total composite channel is obtained by superposing the IRS-aided auxiliary channel to the AP-user direct channel as
			\begin{equation}\label{eq:h_n}
				\boldsymbol{h}_{n}^H = \boldsymbol{h}_{\text{D,}n}^H + \boldsymbol{h}_{\text{R,}n}^H \boldsymbol{\Theta} \boldsymbol{H}_{\text{I,}n} = \boldsymbol{h}_{\text{D,}n}^H + \boldsymbol{\phi}^H \boldsymbol{V}_{n}
			\end{equation}
			where we define $\boldsymbol{\phi} \triangleq [\phi_1, \dots, \phi_L]^H \in \mathbb{C}^{L \times 1}$ and $\boldsymbol{V}_{n} \triangleq \mathrm{diag}(\boldsymbol{h}_{\text{R,}n}^H)\boldsymbol{H}_{\text{I,}n} \in \mathbb{C}^{L \times M}$. Note the conjugate transpose in the notation of $\boldsymbol{\phi}$ makes its entries the complex conjugate of the diagonal entries of $\boldsymbol{\Theta}$.
			\begin{remark}\label{re:irs_frequency_flat}
				Due to hardware constraints, independent phase shift control for different frequencies is prohibited and the IRS is frequency-flat. Hence, the auxiliary channels at different frequencies cannot be simultaneously maximized and there is a tradeoff in subchannel alignment. For each IRS element, the reflection coefficient is shared by $M$ AP-IRS-user channels over $N$ subbands.
			\end{remark}
		\end{subsection}

		\begin{subsection}{Receive Signal}
			At the single-antenna receiver, the total received signal $y(t) \triangleq y_{\text{I}}(t)+y_\text{P}(t)$ captures the contribution from information and power components over all subbands, where
			\begin{align}
				y_{\text{I}}(t) & = \Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{n}^H}{\boldsymbol{w}_{\text{I,}n}\tilde{x}_{\text{I,}n}(t)}{e^{j2{\pi}{f_n}{t}}}\right\}\,,\label{eq:y_I}\\
				y_{\text{P}}(t) & = \Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{n}^H}\boldsymbol{w}_{\text{P},n}{e^{j2{\pi}{f_n}{t}}}\right\}\,.\label{eq:y_P}
			\end{align}
		\end{subsection}

		\begin{subsection}{Information Decoder}
			A major benefit of the superposed waveform is that the multisine power waveform creates no interference to the information waveform. Therefore, the achievable rate writes as
			\begin{equation}\label{eq:R}
				R(\boldsymbol{\phi},\boldsymbol{w}_{\text{I}},\rho) = \sum_{n=1}^N{\log_2\left(1+\frac{(1-\rho)\lvert \boldsymbol{h}_{n}^H\boldsymbol{w}_{\text{I,}n} \rvert^2}{\sigma_n^2}\right)}
			\end{equation}
			where $\rho$ is the power splitting ratio for the energy harvester, $\sigma_n^2$ is the variance of the total noise (at RF-band and during RF-to-baseband conversion) on tone $n$. Rate \eqref{eq:R} is achievable with either waveform cancellation or translated demodulation \cite{Clerckx2018b}.
		\end{subsection}

		\begin{subsection}{Energy Harvester}
			\begin{figure}[!t]
				\centering
				\noindent
				\begin{minipage}[b]{0.5\linewidth}
					\centering
					\subfloat[Antenna equivalent circuit\label{ci:antenna_equivalent_circuit}]{
						\resizebox{0.9\linewidth}{!}{
							\begin{circuitikz}[transform shape]
							\draw (0,0) to [sV=$v_{\text{S}}$] (0,2);
							\draw (0,2) to [short] (1,2);
							\draw (1,2) to [R=$R_\text{ant}$] (3,2);
							\draw (3,2) to [short] (4,2);
							\draw (4,2) to [R=$R_\text{in}$, v<=$v_{\text{in}}$] (4,0);
							\draw (4,0) to [short] (2,0) node[ground](GND){};
							\draw (2,0) to [short] (0,0);
						\end{circuitikz}
						}
					}
				\end{minipage}%
				\begin{minipage}[b]{0.5\linewidth}
					\centering
					\subfloat[A single diode rectifier\label{ci:single_diode_rectifier}]{
						\resizebox{0.9\linewidth}{!}{
							\begin{circuitikz}[transform shape]
							\draw (0,0) to [sV=$v_\text{in}$] (0,2);
							\draw (0,2) to [short] (0.25,2);
							\draw (0.25,2) to [D, v<=$v_{\text{D}}$, i=$i_{\text{D}}$] (2.25,2);
							\draw (2.25,2) to [short, -*] (2.5,2);
							\draw (2.5,2) to [C, l_=$C$, -*] (2.5,0);
							\draw (2.5,2) to [short] (4,2);
							\draw (4,2) to [R=$R_\text{L}$, v<=$v_{\text{out}}$, i=$i_{\text{out}}$] (4,0);
							\draw (4,0) to [short] (2,0) node[ground](GND){};
							\draw (2,0) to [short] (0,0);
						\end{circuitikz}
						}
					}
				\end{minipage}
				\caption{Receive antenna and energy harvester circuits.}
			\end{figure}

			In this section, we briefly revisit a tractable nonlinear rectenna model that relates the harvester output DC current to the received waveform. Fig.~\ref{ci:antenna_equivalent_circuit} illustrates the equivalent circuit of an ideal antenna, where the antenna has an impedance $R_{\text{ant}}$ and the incoming signal creates an voltage source $v_{\text{S}}(t)$. Let $R_{\text{in}}$ be the total input impedance of the rectifier and matching network, and we assume the voltage across the matching network is negligible. When perfectly matched ($R_{\text{in}}=R_{\text{ant}}$), the rectifier input voltage is $v_{\text{in}}(t)=y(t)\sqrt{\rho R_{\text{ant}}}$.

			Rectifiers consist of nonlinear components as diode and capacitor to produce DC output and store energy \cite{Pinuela2013}. Consider a simplified rectifier model in Fig.~\ref{ci:single_diode_rectifier} where a single series diode is followed by a low-pass filter with a parallel load. As detailed in \cite{Clerckx2016a,Clerckx2018b}, a truncated Taylor expansion of the diode I-V characteristic equation suggests that, when the subband frequencies are evenly-spaced, maximizing the average output DC current is equivalent to maximizing a monotonic function \footnote{Note that this small-signal expansion model is only valid for the non-linear operation region, and the I-V relationship would be linear if the diode behavior is dominated by the load \cite{Clerckx2016a}.}
			\begin{equation}\label{eq:z}
				z(\boldsymbol{\phi},\boldsymbol{w}_{\text{I}},\boldsymbol{w}_\text{P},\rho)=\sum_{i\,\text{even},i\ge2}^{n_0}{k_i}{\rho^{i/2}}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{\mathcal{A}\left\{y(t)^i\right\}\right\}}
			\end{equation}
			where $n_0$ is the truncation order and $k_i \triangleq i_{\text{S}}/i!(n'v_{\text{T}})^i$ is the diode coefficient ($i_{\text{S}}$ is the reverse bias saturation current, $n'$ is the diode ideality factor, $v_{\text{T}}$ is the thermal voltage). With a slight abuse of notation, we refer to $z$ as the average output DC current in the following context. It can be observed that the traditional linear harvester model, where the output DC power equals the sum of the power harvested on each frequency, is a special case of \eqref{eq:z} with $n_0=2$. However, due to the coupling among different frequencies, some high-order AC components compensate each other and further contribute to the output DC power. In other words, even-order terms with $i \ge 4$ account for the diode nonlinear behavior. For simplicity, we choose $n_0=4$ to investigate the fundamental rectifier nonlinearity and define $\beta_2 \triangleq {k_2}{R_{\text{ant}}}$, $\beta_4 \triangleq {k_4}{R_{\text{ant}}^2}$ to rewrite $z$ by \eqref{eq:z_expand}. Note that $\mathcal{E}\left\{\lvert\tilde{x}_{\text{I,}n}\rvert^2\right\}=1$ but $\mathcal{E}\left\{\lvert\tilde{x}_{\text{I,}n}\rvert^4\right\}=2$, which can be interpreted as a modulation gain on the nonlinear terms of the output DC current. Inspired by \cite{Huang2017}, we stack up the channel and waveform vectors over all subbands as $\boldsymbol{h} \triangleq [\boldsymbol{h}_1^T,\dots,\boldsymbol{h}_N^T]^T \in \mathbb{C}^{MN \times 1}$ and $\boldsymbol{w}_{\text{I/P}} \triangleq [\boldsymbol{w}_{\text{I/P,}1}^T,\dots,\boldsymbol{w}_{\text{I/P,}N}^T]^T \in \mathbb{C}^{MN \times 1}$, then define $\boldsymbol{W}_{\text{I/P}} \triangleq \boldsymbol{w}_{\text{I/P}}\boldsymbol{w}_{\text{I/P}}^H \in \mathbb{C}^{MN \times MN}$. As illustrated by Fig.~\ref{fi:block_diagonal}, $\boldsymbol{W}_{\text{I/P}}$ can be divided into $N \times N$ blocks of size $M \times M$, and we let $\boldsymbol{W}_{\text{I/P,}k}$ keep its $k$-th ($k=-N+1,\dots,N-1$) block diagonal and set all other blocks to $\boldsymbol{0}^{M \times M}$. Hence, the components of the output DC current $z$ can be expressed in \eqref{eq:y_I2} -- \eqref{eq:y_P4}.

			% Denote $i_{\text{S}}$ as the reverse bias saturation current, $n'$ as the diode ideality factor, $v_{\text{T}}$ as the thermal voltage, $v_{\text{D}}(t)=v_{\text{in}}(t)-v_{\text{out}}(t)$ as the voltage across the diode where $v_{\text{out}}(t)$ is the output voltage across the load. A Taylor expansion of the diode characteristic equation $i_{\text{D}}(t)=i_{\text{S}}(e^{v_{\text{D}}(t)/n' v_{\text{T}}}-1)$ around a quiescent operating point $a$ writes as $i_{\text{D}}(t)=\sum_{i=0}^{\infty}k_i'(v_{\text{D}}(t)-a)^i$, where $k_0'=i_{\text{S}}(e^{a/n' v_{\text{T}}}-1)$ and $k_i'=i_{\text{S}}e^{a/n'v_{\text{T}}}/i!(n'v_{\text{T}})^i$ for $i=1,\dots,\infty$. Note that this small-signal expansion model is only valid for the non-linear operation region, and the I-V relationship would be linear if the diode behavior is dominated by the load \cite{Clerckx2016a}. Also, an ideal low-pass filter with steady-state response can provide a constant $v_{\text{out}}$ that depends on the peak of $v_{\text{in}}(t)$ \cite{Curty2005}. Therefore, a proper choice of the operating voltage drop is $a=\mathcal{E}\{v_{\text{D}}(t)\}=-v_{\text{out}}$ such that
			% \begin{equation}\label{eq:i_D}
			% 	i_{\text{D}}(t)=\sum_{i=0}^{\infty}k_i'\rho^{i/2}R_{\text{ant}}^{i/2}y(t)^i\,.
			% \end{equation}
			% By discarding the non-DC components, taking an expectation over symbol distribution, and truncating \eqref{eq:i_D} to the $n_0$-th order, we approximate the average output DC current for a given channel as
			% \begin{equation}\label{eq:i_out}
			% 	i_{\text{out}}(t)=\mathcal{A}\{i_{\text{D}}(t)\}\approx\sum_{i=0}^{n_0}{k_i'}{\rho^{i/2}}{R_{\text{ant}}^{i/2}}\mathcal{E}\left\{{\mathcal{A}\left\{y(t)^i\right\}}\right\}\,.
			% \end{equation}
			% With the assumption of evenly-spaced frequencies, it holds that $\mathcal{A}\left\{y(t)^i\right\}=0$ for odd $i$ thus the related terms have no contribution to DC output. However, $k_i'$ is still a function of $i_{\text{out}}$, and \cite{Clerckx2016a} proved that maximizing a truncated $i_{\text{out}}$ is equivalent to maximizing a monotonic function
			% \begin{equation}\label{eq:z}
			% 	z(\boldsymbol{\phi},\boldsymbol{w}_{\text{I}},\boldsymbol{w}_\text{P},\rho)=\sum_{i\,\text{even},i\ge2}^{n_0}{k_i}{\rho^{i/2}}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{\mathcal{A}\left\{y(t)^i\right\}\right\}}
			% \end{equation}
